---
title: "Personality_Analysis"
author: "Markus Lundsfryd Jensen"
date: "2025-05-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pacman)

pacman::p_load(tidyverse,
               lme4,
               dplyr,
               ggplot2,
               emmeans)


personality_data = read.csv('./PersonalityData.csv')
```



Scale bold level and change class of 
```{r}
personality_data <-  
  personality_data %>%
  mutate(Candidate = as.factor(Candidate),
         Topic = as.factor(Topic),
         party = as.factor(party),
         bold_level = as.numeric(scale(bold_level)))

topic_counts <- personality_data %>%
  dplyr::count(Topic, name = "count") %>%
  arrange(desc(count))

filtered_data <- personality_data

#OBS: Might not need this
# Filter out topics with fewer than 10 occurrences
#filtered_data <- personality_data %>%
 # group_by(Topic) %>%
  #filter(n() >= 10)


```



```{r}

#plot 10 mosty used topics
personality_data %>% 
  dplyr::count(Topic, name = "n")  %>% 
  arrange(desc(n)) %>%
  slice_head(n = 10) %>% 
  ggplot(aes(x = fct_reorder(Topic, n),
                  y = n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Top 10 Topics by Count",
       x = "Topic",
       y = "Count") +
  theme_minimal()

#ggsave("top10topics.png")

```





**Now make the above with a bayesian approach**


```{r}
model_data <- data.frame(
  bold = filtered_data$bold_level,
  party = as.factor(filtered_data$party),
  topic = as.factor(filtered_data$Topic), 
  candidate = as.factor(filtered_data$Candidate)
)


```


```{r}

#OBS priors for binary variables in rethinking

# rstanarm for multilevel models
library(rstanarm)


#model_data$party <- as.factor(model_data$party)

party_model_stan <- stan_lmer(
  bold ~ 0 + party + (1 | topic),  # 0 + party forces estimation of all levels
  data = model_data,
  prior = normal(0, 1),            # shared prior across all party levels
  prior_intercept = NULL,         # no global intercept needed
  prior_aux = exponential(1), #sigma prior
  prior_covariance = decov(
    scale = 1,                    # mean 0, sd 1 for random effect SDs
    regularization = 1,           # partial pooling; larger = more shrinkage
    concentration = 1             # LKJ prior on correlation matrix (1 = uniform)
  ), #regularisation ontrols the strength of shrinkage on group level effects
  algorithm = "sampling", #sampling is MCMC
  adapt_delta = 0.95, #increasing adapt_delta will result in a smaller step size and fewer divergences
  QR = FALSE  #maybe true for computational purposes
)

```
Look at the chains
```{r}
#Plot some hairy cattepillars

library(rethinking)

library(bayesplot)
launch_shinystan(party_model_stan, ppd = FALSE)

```


```{r}
#Predicted posterior
posterior <- as.data.frame(party_model_stan)
names(posterior)
precis(posterior)
```


```{r}
library(dplyr)
posterior <- posterior %>%
  rename("Democratic" = partyDemocratic,
         "Republican" = partyRepublican)

mcmc_areas(posterior, 
           pars = c("Democratic", "Republican"), 
           prob = 0.95) +
  ggtitle("Posterior distribution of the effects by party")


```

```{r}
library(bayesplot)
library(ggplot2)

summary_stats <- data.frame(
  mean = mean(posterior$party_diff),
  sd = sd(posterior$party_diff),
  lower = quantile(posterior$party_diff, 0.025),
  upper = quantile(posterior$party_diff, 0.975)
)

print(summary_stats)




```



```{r}
# Select relevant columns and pivot to long format
posterior_long <- posterior %>%
  select(Democratic, Republican) %>%
  pivot_longer(cols = everything(), 
               names_to = "Party", 
               values_to = "Effect") %>%
  mutate(Party = recode(Party, 
                        Democratic = "Democrats",
                        Republican = "Republicans"))

# Plot with specified colors
ggplot(posterior_long, aes(x = Effect, fill = Party, color = Party)) +
  geom_density(alpha = 0.4, size = 1) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("Democrats" = "skyblue", "Republicans" = "red")) +
  scale_color_manual(values = c("Democrats" = "skyblue", "Republicans" = "red")) +
  labs(
    title = "Posterior Distributions of Party Effects",
    x = "Effect on Boldness",
    y = "Density"
  ) +
  theme_minimal()

ggsave("posteriorPartyEffects.png", height = 7, width = 7)
```

```{r}
library(ggplot2)

# Compute the posterior difference
posterior$party_diff <- posterior$Republican - posterior$Democratic

# Plot the difference
ggplot(posterior, aes(x = party_diff)) +
  geom_density(fill = "skyblue", alpha = 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Posterior Distribution of the Difference: Republicans − Democrats",
    x = "Difference in Effect",
    y = "Density"
  ) +
  theme_minimal()

ggsave("posteriorDifferencePartyEffect.png")

```

```{r}
names(posterior)
```




Now for the candidates

```{r}


candidate_model_stan <- stan_lmer(
  bold ~ 0 + candidate + (1 | topic),  # 0 + party forces estimation of all levels
  data = model_data,
  prior = normal(0, 1),            # shared prior across all party levels
  prior_intercept = NULL,         # no global intercept needed
  prior_aux = exponential(1), #sigma prior
  prior_covariance = decov(
    scale = 1,                    # mean 0, sd 1 for random effect SDs
    regularization = 1,           # partial pooling; larger = more shrinkage
    concentration = 1             # LKJ prior on correlation matrix (1 = uniform)
  ), #regularisation ontrols the strength of shrinkage on group level effects
  algorithm = "sampling", #sampling is MCMC
  adapt_delta = 0.95, #increasing adapt_delta will result in a smaller step size and fewer divergences
  QR = FALSE  #maybe true for computational purposes
)
```



```{r}
posterior_candidate <- as.data.frame(candidate_model_stan)
names(posterior_candidate)
precis(posterior_candidate)

```


```{r}
library(dplyr)
posterior_candidate <- posterior_candidate %>%
  rename("Biden" = candidatebiden, 
         "Carter" = candidatecarter,
         "Clinton" = candidateclinton,
         "Ford" = candidateford,
         "HW_Bush" = candidatehw_bush,
         "Kenedy" = candidatekennedy,
         "Nixon" = candidatenixon,
         "Obama" = candidateobama,
         "Reagan" =  candidatereagan,
         "Trump" = candidatetrump,
         "W_Bush" = candidatew_bush)

mcmc_areas(posterior_candidate, 
           pars = c("Biden", 
                    "Carter", 
                    "Clinton",
                    "Ford",
                    "HW_Bush",
                    "Kenedy",
                    "Nixon",
                    "Obama",
                    "Reagan",
                    "Trump",
                    "W_Bush"), 
           
           prob = 0.95) +
  
  ggtitle("Posterior distribution of the effects by candidate")+
  
  xlab("Effect size")+
  ylab("President")+
  theme_minimal()+
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50")

  
  
  ggsave("posteriorEffectsCandidate.png", height = 4, width = 7)


```


```{r}
# Select relevant columns and pivot to long format
posterior_long_candidates <- posterior_candidate %>%
  select("Biden", 
                    "Carter", 
                    "Clinton",
                    "Ford",
                    "HW_Bush",
                    "Kenedy",
                    "Nixon",
                    "Obama",
                    "Reagan",
                    "Trump",
                    "W_Bush") %>%
  pivot_longer(cols = everything(), 
               names_to = "Candidate", 
               values_to = "Effect")

# Plot with specified colors
ggplot(posterior_long_candidates, aes(x = Effect, fill = Candidate, color = Candidate)) +
  geom_density(alpha = 0.4, size = 1) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  #scale_fill_manual(values = c("Democrats" = "skyblue", "Republicans" = "red")) +
  #scale_color_manual(values = c("Democrats" = "skyblue", "Republicans" = "red")) +
  labs(
    title = "Posterior Distributions of Candidate Effects",
    x = "Effect on Boldness",
    y = "Density"
  ) +
  theme_minimal()


```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)

# 1. Extract posterior draws for candidates
# Assuming `posterior_candidate` is a dataframe with samples in columns named after candidates

candidates <- c("Biden", "Carter", "Clinton", "Ford", "HW_Bush", "Kenedy", 
                "Nixon", "Obama", "Reagan", "Trump", "W_Bush")

posterior_sub <- posterior_candidate %>% select(all_of(candidates))

# Pivot posterior_sub to long format: samples x candidates
posterior_long <- posterior_sub %>%
  mutate(draw = row_number()) %>%
  pivot_longer(-draw, names_to = "candidate", values_to = "effect")

# Get all candidate names
candidates <- unique(posterior_long$candidate)

# Generate all pairwise candidate pairs
pairs <- combn(candidates, 2, simplify = FALSE)

# Compute differences by joining draws and subtracting effects
diff_list <- map_dfr(pairs, function(pair) {
  lhs <- posterior_long %>% filter(candidate == pair[1]) %>% select(draw, lhs_effect = effect)
  rhs <- posterior_long %>% filter(candidate == pair[2]) %>% select(draw, rhs_effect = effect)
  diff_df <- left_join(lhs, rhs, by = "draw") %>%
    mutate(
      Contrast = paste(pair[1], "vs", pair[2]),
      Difference = lhs_effect - rhs_effect
    ) %>%
    select(Contrast, Difference)
  diff_df
})

# Now diff_list has all pairwise contrasts in long format for plotting etc.

posterior_diffs <- bind_rows(diff_list)

# 3. (Optional) summarize each contrast for plotting intervals
summary_diffs <- posterior_diffs %>%
  group_by(Contrast) %>%
  summarize(
    median = median(Difference),
    lower = quantile(Difference, 0.025),
    upper = quantile(Difference, 0.975)
  ) %>%
  arrange(median)

party_lookup <- tibble(
  candidate = c("Biden", "Carter", "Clinton", "Obama", "Kenedy",
                "Trump", "Reagan", "Nixon", "Ford", "HW_Bush", "W_Bush"),
  party = c("Democrat", "Democrat", "Democrat", "Democrat", "Democrat",
            "Republican", "Republican", "Republican", "Republican", "Republican", "Republican")
)


summary_diffs_labeled <- summary_diffs %>%
  separate(Contrast, into = c("candidate1", "candidate2"), sep = " vs ") %>%
  left_join(party_lookup, by = c("candidate1" = "candidate")) %>%
  rename(party1 = party) %>%
  left_join(party_lookup, by = c("candidate2" = "candidate")) %>%
  rename(party2 = party) %>%
  mutate(
    comparison_type = case_when(
      party1 == party2 & party1 == "Democrat" ~ "Democrat vs Democrat",
      party1 == party2 & party1 == "Republican" ~ "Republican vs Republican",
      party1 != party2 ~ "Democrat vs Republican"
    )
  )





```



plot
```{r}
#Plot contrasts with intervals

ggplot(summary_diffs_labeled, aes(x = median, y = reorder(paste(candidate1, "vs", candidate2), median))) +
  geom_point(aes(color = comparison_type)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper, color = comparison_type), height = 0.3) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  labs(
    title = "95% Credible Intervals for Pairwise Differences Between Candidates",
    x = "Difference in Effect Size",
    y = "Candidate Contrast",
    color = "Comparison Type"
  ) +
  scale_color_manual(values = c(
    "Democrat vs Democrat" = "skyblue",
    "Republican vs Republican" = "firebrick",
    "Democrat vs Republican" = "purple"
  )) +
  theme_minimal()

ggsave("pairwiseCandidates.png", height = 10)
```
#OBS the above might be problematic as there is not being controlled for multiple comparisons?? Bayesian False Discovery Rate (FDR) methods??

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

# 1. Filter contrasts where 95% credible interval excludes 0
significant_diffs <- summary_diffs_labeled %>%
  filter(lower > 0 | upper < 0) %>%
  mutate(Contrast = paste(candidate1, "vs", candidate2))  # Recreate full contrast label for plotting

# 2. Plot only significant contrasts
ggplot(significant_diffs, aes(x = median, y = reorder(Contrast, median))) +
  geom_point(aes(color = comparison_type)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper, color = comparison_type), height = 0.3) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  labs(
    title = "Statistically Credible Pairwise Differences",
    x = "Difference in Effect Size",
    y = "Candidate Contrast",
    color = "Comparison Type"
  ) +
  scale_color_manual(values = c(
    "Democrat vs Democrat" = "skyblue",
    "Republican vs Republican" = "firebrick",
    "Democrat vs Republican" = "purple"
  )) +
  theme_minimal()



ggsave("significantPairwiseCandidates.png", height = 5, width = 6)

```
Only fo the three guys
```{r}
lookup_three_guys <- c("Obama", "Trump", "Biden")
# 1. Filter contrasts where 95% credible interval excludes 0
significant_diffs_2 <- summary_diffs_labeled %>%
  filter((candidate1 %in% lookup_three_guys) & (candidate2 %in% lookup_three_guys)) %>% 
  mutate(Contrast = paste(candidate1, "vs", candidate2))

# 2. Plot only significant contrasts
ggplot(significant_diffs_2, aes(x = median, y = reorder(Contrast, median))) +
  geom_point(aes(color = comparison_type), size = 2) +
  geom_errorbarh(aes(xmin = lower, xmax = upper, color = comparison_type), height = 0.15, linewidth = 1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  labs(
    title = "Pairwise Differences of Obama, Biden and Trump",
    x = "Difference in Effect Size",
    y = "Candidate Contrast",
    color = "Comparison Type"
  ) +
  scale_color_manual(values = c(
    "Democrat vs Democrat" = "skyblue",
    "Republican vs Republican" = "firebrick",
    "Democrat vs Republican" = "purple"
  )) +
  theme_minimal()

ggsave("pairwise_threeGuys.png", height = 5, width = 6)
```



All good

*Do something with the topics. Maybe check how different values of bold are apparent in different topics - what topics are highest in bold maybe interaction between this and party? Also some simple stuff: what topics are most presently discussed (maybe over time). Also include, maybe just some short statistics, about the level of similarity, now that we have it.*

Now for some topics stuff, only working with party model
```{r}
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)

# Extract all topic-level intercept columns
topic_effects <- posterior %>%
  select(starts_with("b[(Intercept) topic:")) %>%
  pivot_longer(cols = everything(), names_to = "topic", values_to = "effect")

# Clean up topic names
topic_effects <- topic_effects %>%
  mutate(topic = str_remove_all(topic, "r_topic\\[|,Intercept\\]"))

```

```{r}

library(stringr)

topic_summary <- topic_effects %>%
  mutate(topic = str_replace(topic, "^b\\[\\(Intercept\\) topic:", "")) %>%
  mutate(topic = str_replace(topic, "\\]$", "")) %>%
  mutate(topic = str_replace_all(topic, "_", " ")) %>%
  group_by(topic) %>%
  summarize(
    median = median(effect),
    lower = quantile(effect, 0.025),
    upper = quantile(effect, 0.975)
  ) %>%
  arrange(median)

```


```{r}
ggplot(topic_summary, aes(x = median, y = reorder(topic, median))) +
  geom_point(color = "black") +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2, color = "darkgray") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Posterior Topic-Level Effects with Shrinkage",
    x = "Estimated Topic Effect (Random Intercept)",
    y = "Topic"
  ) +
  theme_minimal()

ggsave("plot.png", height = 10, width = 8)

```

Once again

```{r}
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)

# Create domain mapping (based on your documentation)
domain_map <- tibble(
  domain = 1:7,
  domain_label = c(
    "Domain 1: External Relations",
    "Domain 2: Freedom and Democracy",
    "Domain 3: Political System",
    "Domain 4: Economy",
    "Domain 5: Welfare and Quality of Life",
    "Domain 6: Fabric of Society",
    "Domain 7: Social Groups"
  ),
  domain_color = c("red", "blue", "green", "orange", "purple", "brown", "pink")
)

# Filter topic-level intercepts and extract domain
posterior_long <- posterior %>%
  select(starts_with("b[(Intercept) topic:")) %>%
  pivot_longer(cols = everything(), names_to = "param", values_to = "effect") %>%
  mutate(
    topic = str_replace(param, "^b\\[\\(Intercept\\) topic:", ""),
    topic = str_replace(topic, "\\]$", ""),
    topic_clean = str_replace_all(topic, "_", " "),
    topic_number = as.integer(str_extract(topic, "^\\d+")),
    domain = floor(topic_number / 100)
  ) %>%
  left_join(domain_map, by = "domain")

# Summarize posterior
topic_summary <- posterior_long %>%
  group_by(topic_clean, domain_label, domain_color) %>%
  summarize(
    median = median(effect),
    lower = quantile(effect, 0.025),
    upper = quantile(effect, 0.975),
    .groups = "drop"
  ) %>%
  arrange(median)

# Plot
ggplot(topic_summary, aes(x = median, y = reorder(topic_clean, median), color = domain_label)) +
  geom_point() +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.3) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  scale_color_manual(values = setNames(domain_map$domain_color, domain_map$domain_label)) +
  labs(
    title = "Posterior Topic-Level Effects by Domain",
    x = "Effect Size",
    y = "Topic",
    color = "Domain"
  ) +
  theme_minimal()

ggsave("topiclevelEffects.png", height = 10, width = 8)
```

```{r}
library(dplyr)
library(ggplot2)

# Step 1: Remove duplicates so each candidate has only one score per topic
unique_scores <- personality_data %>%
  distinct(Candidate, Topic, .keep_all = TRUE)

# Step 2: Calculate mean and 95% confidence intervals for each topic
topic_summary <- unique_scores %>%
  group_by(Topic) %>%
  summarize(
    mean_score = mean(Similarity_Score, na.rm = TRUE),
    lower_ci = mean_score - qt(0.975, df = n() - 1) * sd(Similarity_Score) / sqrt(n()),
    upper_ci = mean_score + qt(0.975, df = n() - 1) * sd(Similarity_Score) / sqrt(n())
  ) %>%
  arrange(desc(mean_score))

# Step 3: Plot using ggplot2
ggplot(topic_summary, aes(x = mean_score, y = reorder(Topic, mean_score))) +
  geom_point() +
  geom_errorbarh(aes(xmin = lower_ci, xmax = upper_ci), height = 0.3) +
  labs(
    title = "Mean Similarity Score by Topic (with 95% CI)",
    x = "Mean Similarity Score",
    y = "Topic"
  ) +
  theme_minimal()

ggsave("similarityscoreTopics.png")
```

```{r}
library(dplyr)
library(ggplot2)

# Step 1: One similarity score per Candidate-Topic pair
unique_scores <- personality_data %>%
  distinct(Candidate, Topic, .keep_all = TRUE)

# Step 2: Calculate summary stats
topic_summary <- unique_scores %>%
  group_by(Topic) %>%
  summarize(
    mean_score = mean(Similarity_Score, na.rm = TRUE),
    lower_ci = mean_score - qt(0.975, df = n() - 1) * sd(Similarity_Score) / sqrt(n()),
    upper_ci = mean_score + qt(0.975, df = n() - 1) * sd(Similarity_Score) / sqrt(n())
  ) %>%
  arrange(desc(mean_score))

# Plot 1: With 95% confidence intervals
plot_with_ci <- ggplot(topic_summary, aes(x = mean_score, y = reorder(Topic, mean_score))) +
  geom_point() +
  geom_errorbarh(aes(xmin = lower_ci, xmax = upper_ci), height = 0.3) +
  labs(
    title = "Mean Similarity Score by Topic (with 95% CI)",
    x = "Mean Similarity Score",
    y = "Topic"
  ) +
  theme_minimal()

# Plot 2: Without confidence intervals
plot_without_ci <- ggplot(topic_summary, aes(x = mean_score, y = reorder(Topic, mean_score))) +
  geom_point(color = "steelblue") +
  labs(
    title = "Mean Similarity Score by Topic",
    x = "Mean Similarity Score",
    y = "Topic"
  ) +
  theme_minimal()

# Print both plots
print(plot_with_ci)
print(plot_without_ci)

ggsave("meanSimilarityScoreTopic.png")

```



**Skraldespand **

```{r}
alist <- alist(Bold ~dnorm(mu, sigma),
               mu <- a[Party],
               )
simple_party_model <- quap(alist, data = dat_list)



simple_party_model<- quap(
  alist(
    Bold ~ dnorm( mu , sigma ) ,
    mu <- a[Party] ,
    a[Party] ~ dnorm( 0 , 1 ) ,
    sigma ~ exponential(1)), data=dat_list )


precis( m5.8 , depth=2 )

# Extract samples
posterior <- extract.samples(party_model)

# If you used b_party[P] as a group mean for each party (say 1 = Democrat, 2 = Republican):
diff_posterior <- posterior$b_party[,2] - posterior$b_party[,1]

# Plot the posterior difference
dens(diff_posterior, col = "skyblue", lwd = 2)
abline(v = 0, col = "red", lty = 2)





model_data$N_topic <- length(unique(model_data$topic))

simple_party_model <- quap(
alist(
bold ~ dnorm( mu , sigma ) ,
mu <- a[party] ,
a[party] ~ dnorm(0 , 1 ) ,
sigma ~ dexp(1)
) , data=model_data )



precis( simple_party_model , depth=2 )

multilevel_model <- quap(
  alist(
    bold ~ dnorm(mu, sigma),
    mu <- a[party] + z[topic],
    
    # Fixed effects
    a[party] ~ dnorm(0, 1),
    
    # Random intercepts for topic
    z[topic] ~ dnorm(mu_z, sigma_topic),
    mu_z <- 0,
    sigma_topic ~ dexp(1),
    
    # Observation-level noise
    sigma ~ dexp(1)
  ),
  data = model_data
)
```

make lmer model that predicts bold level by party

```{r}
party_model <- lmerTest::lmer(bold_level ~  party +(1|Topic), data = filtered_data)
summary(party_model)
```
```{r}
emm_party <- emmeans(party_model, ~ party)
emm_party_df <- as.data.frame(emm_party)
```


```{r}


ggplot(emm_party_df, aes(x = party, y = emmean, fill = party)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = c("Democratic" = "#2E86AB", "Republican" = "#D64550")) +
  ylab("Estimated Bold Level") +
  xlab("Party") +
  theme_minimal() +
  theme(legend.position = "none")

```



```{r}
candidate_model <- lmerTest::lmer(bold_level ~  Candidate  +(1|Topic), data = filtered_data)
summary(candidate_model)
```
```{r}

# Get estimated marginal means for each candidate
emm <- emmeans(candidate_model, ~ Candidate)

# Pairwise comparisons between all candidates
pairs(emm)

```
#What values were significant?*

```{r}
# obama - trump       0.5687 0.1040 1409   5.471  <.0001
# obama - w_bush      0.5473 0.0957 1405   5.721  <.0001
# obama - reagan      0.4491 0.1180 1403   3.812  0.0067
#  hw_bush - obama    -0.4751 0.1010 1402  -4.704  0.0001
# clinton - trump     0.3682 0.1130 1404   3.251  0.0461
# clinton - w_bush    0.3468 0.1060 1398   3.266  0.0440
#carter - obama     -0.4329 0.1150 1398  -3.757  0.0082
# biden - nixon      -0.5287 0.1510 1403  -3.490  0.0213
# biden - obama      -0.6774 0.1110 1395  -6.091  <.0001
# biden - clinton    -0.4769 0.1200 1395  -3.964  0.0037
```

Do some visualization: 


```{r}
emm_df <- as.data.frame(emm)

# Get unique candidate-party mapping
party_map <- filtered_data %>%
  select(Candidate, party) %>%
  distinct()

# Join with emm_df
emm_df <- left_join(emm_df, party_map, by = "Candidate")

ggplot(emm_df, aes(x = Candidate, y = emmean, color = party)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2) +
  ylab("Estimated Bold Level") +
  scale_color_manual(values = c("Democratic" = "#2E86AB", "Republican" = "#D64550")) +
  theme_minimal() +
  theme(legend.position = "top")
```
